Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-29 paper/AlignedIsotropicGW.tex
Minor tweaks (address).

\affiliation{Birmingham Institute for Gravitational Wave Astronomy and
  School of Physics and Astronomy, University of Birmingham,
  Birmingham, B15 2TT, United Kingdom}
\affiliation{Kavli Institute of Theoretical Physics, University of California, Santa Barbara}

@@

In summary, the angular distribution of spins in \acp{BBH} formed
through isolated binary evolution is uncertain; nevertheless, it is
more probable that spins are preferentially aligned after evolution
through this channel than not, while an isotropic distribution of
spins is the natural outcome of dynamical formation processes.
Therefore, if the current observational trend for low $\chieff$
continues with future gravitational-wave observations, it will be
possible to either confirm that \ac{BH} spins are sometimes large in
magnitude and isotropic in direction, yielding a strong indication of
a dynamical formation origin; or that \ac{BH} spins are overwhelmingly
small in magnitude, yielding a notable contradiction with the claimed
X-ray binary spin measurements, particularly those for high-mass X-ray
binaries.

>>>>

\affiliation{Birmingham Institute for Gravitational Wave Astronomy and
  School of Physics and Astronomy, University of Birmingham,
  Birmingham, B15 2TT, United Kingdom}
\affiliation{Kavli Institute for Theoretical Physics, Santa Barbara, CA 93106}

@@

In summary, the angular distribution of spins in \acp{BBH} formed
through isolated binary evolution is uncertain; nevertheless, it is
more probable that spins are preferentially aligned after evolution
through this channel than not, while an isotropic distribution of
spins is the natural outcome of dynamical formation processes.
Therefore, if the current observational trend for low $\chieff$
continues with future gravitational-wave observations, it will be
possible to either confirm that \ac{BH} spins are sometimes large in
magnitude and isotropic in direction, yielding a strong indication of
a dynamical formation origin; or that \ac{BH} spins are overwhelmingly
small in magnitude, yielding a notable contradiction with the claimed
\ac{BH} X-ray binary spin measurements, particularly those for high-mass X-ray
binaries.
